Differential invariant signatures for planar Lie group transformations of images

### 2020-11-17 paper/newpaper.tex
getting there

\section{Introduction}
\todo[inline]{
Abstract
Bad set, singular
Literature
Weight

Example intro
T(2)

Sim(2) by contraction
A(2) by transvectant

When introduce each group, mention relevance to images?

Friendly intro to moving frame
Finish colour

Discussion
}

@@

An $m$-dimensional signature set is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e., the set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.  A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$. If the signature is not complete, then there will be a \emph{bad set} of images that cannot be differentiated between. ***

NEED TO TALK ABOUT WHEN IT IS SINGULAR

For the case of two-dimensional greyscale images it is often convenient to work in coordinates. In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by:
\begin{equation}\label{eq:transformation}
  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x}).
\end{equation}
The transformed image is then defined to be:
\begin{equation}\label{eq:fbarequalsf}
  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
\end{equation}
Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
\begin{equation}\label{eq:prolongation}
  \begin{aligned}
    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
  \end{aligned}
\end{equation}
where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. %It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.

@@

@@

\subsection{Getting Started: Translations}

The most basic transformation group of a image is the translation group $T(2): \phi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$.

@@

\section{Differential invariants through tensor contraction}

@@

The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor. \todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.

@@

\todo[inline]{Expand to Sim(2)}
\todo[inline]{Introduce image that we are going to use in subsequent examples}
\todo[inline]{Introduce signatures - 3D and 4D perhaps?}

@@

Under this formula we end with a factor $(\det A)^{-r}$ in place of $(\det
A)^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
\mathbf{b}$. $r$ is referred to as the weight of the partial
transvectant. Note that the individual pairwise Omega processes commute.
The concept of a relative invariant will be important in what follows.

@@

For example, consider a weight $2$ transvectant defined as:
\begin{align*}
    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
    &= \mbox{tr} 2 \left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
    &= 2 f_{xx}(x, y) f_{yy}(x, y) - 2 f_{xy}(x, y)^2.
\end{align*}
This is a degree $2$ partial transvectant as it involves derivatives of $f$
up to second-order, and can be represented graphically by the following
diagram:
\begin{center}
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
\end{center}
where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$ (the names are purely for convenience).

@@

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\

2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{yy} - 2 f_{x} f_{y} f_{xy} + f_{xx}
\left(f_{y}\right)^{2}$ \\

2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (1);
\end{tikzpicture}
& $2 \left(f_{xx}\right)^{2} \left(f_{yy}\right)^{2} - 4 f_{xx} f_{yy} \left(f_{xy}\right)^{2} + 2 \left(f_{xy}\right)^{4}$ \\

2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\

3 & 3 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\

3 & 3 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
    \draw[-] (2) to (3);
\end{tikzpicture}
& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\

@@

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
\end{tikzpicture}
& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\

% =========
3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants1}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
    \draw[-] (1) to [out=10,in=170] (2);
    \draw[-] (1) to [out=-10,in=-170] (2);
\end{tikzpicture}
& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to [out=-90,in=150] (3);
    \draw[-] (1) to [out=-30,in=90] (3);
\end{tikzpicture}
& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\

>>>>

\section{Introduction}
\todo[inline]{
Abstract
Literature

Sim(2) by contraction
A(2) by transvectant
Check signatures for Mobius etc.

Discussion

Make table fit

}

@@

An $m$-dimensional signature set is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e., the set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$. See Section~\ref{sec:T2} for a basic example.  A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$. If the signature is not complete, then there will be a \emph{bad set} of images that cannot be differentiated between.

The methods we use to construct the invariants, particularly the moving frames, produces invariants that, when considered alone, are singular at certain points (for example, critical points). However, in all groups considered the invariants are rational functions of the derivatives of the function. Moreover, the denominators of these functions are powers of each other, and so it is possible to clear them, thus removing these singular points by a projection technique that will be introduced in Section~\ref{sec:Sim2}.

For the case of two-dimensional greyscale images it is often convenient to work in coordinates. In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by:
\begin{equation}\label{eq:transformation}
  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x}).
\end{equation}
The transformed image is then defined to be:
\begin{equation}\label{eq:fbarequalsf}
  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
\end{equation}

Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
\begin{equation}\label{eq:prolongation}
  \begin{aligned}
    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
  \end{aligned}
\end{equation}
where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. %It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.

@@

\subsubsection{Example}
Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
defined on $[0, 1]\times[0, 1]$.

@@

\subsection{Getting Started: Translations}
\label{sec:T2}

The most basic transformation group of a image is the translation group $T(2): \phi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$. These could arise from actions such as cropping a photo.

@@

\section{Differential invariants through tensor contraction}
\label{sec:contraction}

@@

The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor~\cite{Florack1993}. Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.

@@

SE(2): rotation, Sim(2): zooming.

@@

Under this formula we end with a factor $(\det A)^{-r}$ in place of $(\det
A)^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
\mathbf{b}$. $r$ is referred to as the weight of the partial
transvectant. Note that the individual pairwise Omega processes commute.

The concept of a relative invariant will be important in the rest of this paper. It follows the definition given here, except that the function weighting the invariant is more general, see~\cite{Fels1997} for more details. In contrast to that paper, we will continue to use the term weight to represent the power to which the function is raised.

@@

For example, consider a weight $2$ transvectant defined as:
\begin{align*}
    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
    &= \mbox{tr} 2 \left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
    &= 2 f_{xx}(x, y) f_{yy}(x, y) - 2 f_{xy}(x, y)^2.
\end{align*}
This is a degree $2$ partial transvectant as it involves derivatives of $f$
up to second-order, and can be represented graphically by the following
diagram:
\begin{center}
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
\end{center}
where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$ (the names are purely for convenience).

@@

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\

2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (0.5,0) {3};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{yy} - 2 f_{x} f_{y} f_{xy} + f_{xx}
\left(f_{y}\right)^{2}$ \\

2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.15cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (1);
\end{tikzpicture}
& $2 \left(f_{xx}\right)^{2} \left(f_{yy}\right)^{2} - 4 f_{xx} f_{yy} \left(f_{xy}\right)^{2} + 2 \left(f_{xy}\right)^{4}$ \\

2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.15cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.15cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\

3 & 3 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\

3 & 3 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.15cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
    \draw[-] (2) to (3);
\end{tikzpicture}
& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\

@@

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.15cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
\end{tikzpicture}
& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.15cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\

% =========
3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.15cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.15cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants1}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
    \draw[-] (1) to [out=10,in=170] (2);
    \draw[-] (1) to [out=-10,in=-170] (2);
\end{tikzpicture}
& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to [out=-90,in=150] (3);
    \draw[-] (1) to [out=-30,in=90] (3);
\end{tikzpicture}
& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.15cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.15cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.15cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture} 
& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
